# ENACT {#sec-enact_data_preparation}

## Data preparation process

The data preparation process is as follows:

1.  Run loyalty cohort using settings on 2020-01-01 and a 3-year lookback.\
    \* More information about [loyalty cohort algorithm](https://github.com/i2b2plugins/loyalty_cohort)
2.  Download the [CCSR_PASC_ACT_Mapping_022024.csv](https://github.com/clai-group/long_covid_ai_scripts/blob/main/CCSR_PASC_ACT_Mapping_022024.csv)
3.  Pall patients with a COVID positive lab test or a COVID diagnosis, pull loyalty scores for these patients and cut the initial patient sets to those with a loyalty score \> 0.3.\
    \* Query script: [ExportCases.sql](https://github.com/clai-group/long_covid_ai_scripts/blob/main/ExportCases.sql)
4.  Pull patient data and demographics for the updated cases starting on 2017-01-01.\
    \* Query script: [ExportDemCases.sql](https://github.com/clai-group/long_covid_ai_scripts/blob/main/ExportDemCases.sql)

## Table example

Tables we need should have these columns:

**Patient data** (should be saved as **cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","start_date", "concept_cd","c_fullname", "phenx"),
                   c("num","date (yyyy-mm-dd)", "char","char", "char"))
)
```

**Demographic data** (should be saved as **dems_cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","age", "sex_cd", "race_cd",  "ethnicity_cd", "CHARLSON_INDEX"),
                   c("num","num","char (F/M)", "char", "char", "num"))
)
```

## Directory guide

Recommended directory tree on the server/device where docker is running in the next step:

-   PASC

    -   data

        -   cases

            -   **cases.csv**
            -   **dems_cases.csv**

    -   output
