# ENACT {#sec-enact_data_preparation}

## Data preparation process

The data preparation process is as follows:

1.  Request patient sets for the shrine query (who_pasc_cases) using your local i2b2\
    Query: cases -- include all patients with a COVID + lab test or a COVID diagnosis
2.  Pull patient numbers from the query.
3.  Pull loyalty scores for these patients and cut the initial patient sets to those with a loyalty score \> 0.3.
4.  Pull patient data and demographics for the updated cases starting in 01-01-2017.

## Query example

## Table example

Tables we need should have these columns:

**Patient data** (should be saved as **cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","start_date", "concept_cd", "phenx", "ICD10_desc"),
                   c("character","date", "character", "character", "character" ))
)
```

**Demographic data** (should be saved as **dems_cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","age", "sex_cd", "race_cd",  "ethnicity_cd", "CHARLSON_INDEX"),
                   c("character","date","character", "character", "character", "character"))
)
```


## Directory guide

Recommended directory tree on the server/device where docker is running in the next step:

-   PASC

    -   data

        -   **cases.csv**
        -   **dems_cases.csv**

    -   output
