# Non-ENACT {#sec-non-enact_data_preparation}

## Data preparation process

The data preparation process is as follows:

1.  Query the case data set -- include all patients with a positive lab test or a COVID diagnosis starting in 01-01-2017.
2.  Query patient demographics data -- include sex, age, race, ethnicity and CHARLSON_INDEX.

## Table example

Tables we need should have these columns:

**Patient data** (should be saved as **cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","start_date", "ICD10", "domain"),
                   c("character","date", "character", "character"))
)
```


**Demographic data** (should be saved as **dems_cases.csv**)

```{r,echo=FALSE,warning=FALSE}
knitr::kable(
  rbind(c("patient_num","age", "sex_cd", "race_cd", "ethnicity_cd", "CHARLSON_INDEX"),
                   c("character","date","character", "character", "character", "character"))
)
```

## Directory guide

Recommended directory tree on the server/device where docker is running in the next step:

-   PASC
    -   data
        -   **cases.csv**
        -   **dems_cases.csv**
    -   output
